---
title: "Hw 5 p8105"
author: "Rebecca Silva"
date: "11/07/2019"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(viridis)
library(p8105.datasets)
library(kableExtra)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	message = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
theme_set(theme_minimal() + theme(legend.position = "bottom"))
```


** delete unused packages

### Problem 1 

```{r}
set.seed(10)

iris_with_missing = iris %>% 
  map_df(~replace(.x, sample(1:150, 20), NA)) %>%
  mutate(Species = as.character(Species))

input = iris_with_missing$Sepal.Length

fill_missing = function(vec){
  if(is.numeric(vec)){
    ifelse(is.na(vec), mean(vec, na.rm = T), vec)
  }else{
    ifelse(is.na(vec), "virginica", vec)
  }
}

iris_filled = map(iris_with_missing, fill_missing)

```


### Problem 2 
# Start with a dataframe containing all file names; the list.files function will help
# Iterate over file names and read in data for each subject using purrr::map and saving the result as a new variable in the dataframe
# Tidy the result; manipulate file names to include control arm and subject ID, make sure weekly observations are “tidy”, and do any other tidying that’s necessary
```{r}
df = tibble(
  names = list.files("data 4")
)
tidy_df = 
  df %>% 
  mutate(patient = map(str_c("./data 4/",names), read.csv)) %>% 
  unnest(cols = c(patient)) %>% 
  mutate(n = c(1:nrow(.))) %>% 
  separate(names, 
           into = c("arm", "id"), 
           sep = "_") %>% 
  pivot_longer(
    week_1:week_8, 
    names_to = "week", 
    values_to = "value"
  ) %>% 
  mutate(week = as.numeric(str_remove(week, "week_")), 
         id = as.numeric(str_remove(id, ".csv")))
```

```{r}
# spaghetti plot 
tidy_df %>% 
  mutate(id_arm = str_c(arm, id, sep = "_")) %>% 
  ggplot(aes( x = week, y = value, color = id_arm)) + 
  geom_line(aes(group = id_arm, linetype = arm)) + 
  theme(legend.position = "bottom") +
  labs(
    title = "Observation for each subject over 8 weeks",
    x = "Week",
    y = "Observation") +
  theme(plot.title = element_text(hjust = 0.5)) +
  guides(color = FALSE) +
  scale_linetype_discrete(name = "Arm", labels = c("control", "experimental"))
```

The spaghetti plot shows that over the course of 8 weeks individual's observations in the experimental group increase while individual's observations in the control group tend to stay fluctuating around lower observations and may even decrease.  


